PANCHANGE_analysis

### 2021-03-09 PANCHANGE_analysis.Rmd
updated figure height and width for forest plots

## Forest plots
### disorder
```{r forest plot by disorder prepan, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by disorder retro, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by disorder no explan, fig.height=40, fig.width=60, dpi=120}

@@

### disorder (no PCL)
```{r forest plot by disorder prepan no pcl, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by disorder retro no pcl, fig.height=40, fig.width=60, dpi=120}

@@

### time point 
```{r forest plot by time point gad, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by time point phq, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by time point pcl, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by sample retro only gad, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by sample retro only phq, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by sample no explan gad, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by sample no explan phq, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by sample no explan pcl, fig.height=40, fig.width=60, dpi=120}

>>>>

## Forest plots
### disorder
```{r forest plot by disorder prepan, fig.height=70, fig.width=55, dpi=120}

@@

```{r forest plot by disorder retro, fig.height=70, fig.width=55, dpi=120}

@@

```{r forest plot by disorder no explan, fig.height=70, fig.width=55, dpi=120}

@@

### disorder (no PCL)
```{r forest plot by disorder prepan no pcl, fig.height=70, fig.width=55, dpi=120}

@@

```{r forest plot by disorder retro no pcl, fig.height=70, fig.width=55, dpi=120}

@@

### time point 
```{r forest plot by time point gad, fig.height=70, fig.width=55, dpi=120}

@@

```{r forest plot by time point phq, fig.height=70, fig.width=55, dpi=120}

@@

```{r forest plot by time point pcl, fig.height=70, fig.width=55, dpi=120}

@@

```{r forest plot by sample retro only gad, fig.height=70, fig.width=55, dpi=120}

@@

```{r forest plot by sample retro only phq, fig.height=70, fig.width=55, dpi=120}

@@

```{r forest plot by sample no explan gad, fig.height=70, fig.width=55, dpi=120}

@@

```{r forest plot by sample no explan phq, fig.height=70, fig.width=55, dpi=120}

@@

```{r forest plot by sample no explan pcl, fig.height=70, fig.width=55, dpi=120}
